\section{Program Stubs and Test Data Required}
As we already said in section 2, we used a bottom-up approach with our testing strategy,
therefore we utilized drivers instead of stubs.
\subsection{Request Driver}
The Request Driver is needed to test the correct functioning of the queue. In particular this driver
is used to trigger the retrieval of the first taxi in the queue to whom the dummy request should be
submitted. The dummy request will be made ad-hoc to trigger the method on the desired queue.
\subsection{Guest Driver}
The Guest Driver is needed to test the correct functioning of the Request interface. In particular
this driver is used to create a request by a dummy Guest, that will insert random data to see if the request
is generated correctly.
\subsection{RegisteredPassenger Driver}
The RegisteredPassenger Driver is needed to test the correct function of the Request interface.
In particular this driver is used to create a Request by a dummy RegisteredPassenger,
to see if the request is generated correctly. Also it is indirectly used during the test of
the reservation since a reservation triggers a request once its time comes.
\subsection{TaxiDriver Driver}
The TaxiDriver Driver is needed to test the correct function of the TaxiRequest interface, and also to
test the correct functioning of the queue. In particular this driver is used to give a positive answer or a negative one
by a dummy TaxiDriver to a given request: in case of negative answer the TaxiDriver has to be put again in queue in the last
position, while in case of positive answer the the system will ensure that the TaxiDriver is no longer in queue.
The other use of this driver is to send an input to the system using the method SetAvailable or SetUnavailable. In the first case
the TaxiDriver will be added in queue while in the second one the TaxiDriver will be removed from the queue.
